%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Developer} % Job title
    {KMD} % Organization
    {Ballerup, Denmark} % Location
    {Aug. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a .NET developer on different services used by health clinics.}
        \item {As part of the Research \& Development team I help innovate on a range of different solutions.}
        \item {Setup various application monitoring systems and CI/CD pipeline integrations.}
        \item {Deployed applications on Microsoft Azure and frequently help maintain services.}
        \item {Recently begun doing data analytics and being involved in machine-learning activities.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software developer \& Architect} % Job title
    {Polyteknisk Forening} % Organization
    {Kongens Lyngby, Denmark} % Location
    {Mar. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Currently building a mobile application using React Native and collaborating on building an information platform for the students at DTU.}
        \item {Implemented RESTful API server for the mobile application with support for GraphQL.}
        \item {Together with a design \& innovation engineering student we make up the little team with high hopes for the project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Assistant} % Job title
    {Cobham PLC.} % Organization
    {Kongens Lyngby, Denmark} % Location
    {Aug. 2017 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the Aviator S. project (Testing avionics) with Airbus as customer.}
        \item {Dealing with automating test systems.}
        \item {Worked with Linux \& Docker containers.}
        \item {Used Python to create a lot of scripts.}
      \end{cvitems}
    }

\end{cventries}
